R for Clinical Study Reports and Submission

### 2021-10-27 submission-package.Rmd
use sentence case instead of title case for headings; run styler on Rmds

# Submission Package {#submission-package}

@@

## The Whole Game

@@

## Practical Considerations for R Package Submissions

@@

### Source Location

@@

### Dependency Locations

@@

### R Version

@@

### Package Repo Version

@@

### System Environments

@@

## Prepare R Packages for Submission

@@

## Prepare Analysis Programs for Submission

@@

```{r, eval=FALSE}
knitr::purl(
  "tlf-01-disposition.Rmd",
  output = "esub/analysis/adam/programs/tlf-01-disposition.txt"
)
```

Repeat this for all the R Markdown files.

@@

@@

2. Define Working Directory

@@

3. Specify R Package Repository

@@

4. Install Open-Source R Packages

@@

5. Install Proprietary R Packages

@@

7. Execute Analysis Program

>>>>

# Submission package {#submission-package}

@@

## The whole game

@@

## Practical considerations for R package submissions

@@

### Source location

@@

### Dependency locations

@@

### R version

@@

### Package repo version

@@

### System environments

@@

## Prepare R Packages for submission

@@

## Prepare analysis programs for submission

@@

```{r, eval=FALSE}
input_path <- "~/esubdemo/vignettes/"
output_path <- "~/ectddemo/m5/datasets/ectddemo/analysis/adam/programs/"
knitr::purl(file.path(input_path, "tlf-01-disposition.Rmd"), output = file.path(output_path, "tlf-01-disposition.txt"))
knitr::purl(file.path(input_path, "tlf-02-population.Rmd"), output = file.path(output_path, "tlf-02-population.txt"))
knitr::purl(file.path(input_path, "tlf-03-baseline.Rmd"), output = file.path(output_path, "tlf-03-baseline.txt"))
knitr::purl(file.path(input_path, "tlf-04-efficacy.Rmd"), output = file.path(output_path, "tlf-04-efficacy.txt"))
knitr::purl(file.path(input_path, "tlf-05-ae-summary.Rmd"), output = file.path(output_path, "tlf-05-ae-summary.txt"))
knitr::purl(file.path(input_path, "tlf-06-ae-spec.Rmd"), output = file.path(output_path, "tlf-06-ae-spec.txt"))
```

Run this on all the R Markdown files under `vignettes/`.

@@

To automate this process:

```{r, eval=FALSE}
header <- readLines(textConnection("# Note to Reviewer
# To rerun the code below, please refer to the ADRG appendix.
# After the required packages are installed,
# the path variable needs to be defined by using the example code below.
#
# path = list(adam = \"/path/to/esub/analysis/adam/datasets\") # Modify to use actual location
# path$outtable = path$outgraph = \".\" # Outputs saved to the current folder"))

append_header <- function(file, header) {
  x <- readLines(file)
  y <- c(header, "\n", x)
  writeLines(y, con = file)
  invisible(file)
}

file.path(output_path, "tlf-01-disposition.txt") %>% append_header(header)
file.path(output_path, "tlf-02-population.txt") %>% append_header(header)
file.path(output_path, "tlf-03-baseline.txt") %>% append_header(header)
file.path(output_path, "tlf-04-efficacy.txt") %>% append_header(header)
file.path(output_path, "tlf-05-ae-summary.txt") %>% append_header(header)
file.path(output_path, "tlf-06-ae-spec.txt") %>% append_header(header)
```

@@

2. Define working directory

@@

3. Specify R package repository

@@

4. Install open-source R packages

@@

5. Install proprietary R packages

@@

7. Execute analysis program
